---
title: "03 Automated Machine Learning with H20"
date: "2021-01-06"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
# 03 Automated Machine Learning with H20

Last compiled: `r Sys.Date()`

 

## Automated Machine Learning with H20 (I)


Question #1: Compensation Features What can you deduce about the interaction between Monthly Income and Attrition?
c. Those that are leaving have a lower Monthly Income

Question #2:Compensation Features What can you deduce about the interaction between Percent Salary Hike and Attrition?
d. It's difficult to deduce anything based on the visualization


Question #3:Compensation Features What can you deduce about the interaction between Stock Option Level and Attrition?
c.It’s difficult to deduce anything based on the visualization

Question #4:Survey Results What can you deduce about the interaction between Environment Satisfaction and Attrition?
c. It's difficult to deduce anything based on the visualization

Question #5:Survey Results What can you deduce about the interaction between Work Life Balance and Attrition
b. Those that are leaving have higher density of 2’s and 3’s

Question #6:Performance Data What Can you deduce about the interaction between Job Involvement and Attrition?
d. It's difficult to deduce anything based on the visualization

Question #7:Work-Life Features What can you deduce about the interaction between Over Time and Attrition?
b. The proportion of those staying that are working Over Time are high compared to those that are not staying

Question #8:Training and Education What can you deduce about the interaction between Training Times Last Year and Attrition
b. People that leave tend to have less annual trainings

Question #9:Time-Based Features What can you deduce about the interaction between Years At Company and Attrition
b. People that leave tend to have less working years at the company

Question #10:Time-Based Features What can you deduce about the interaction between Years Since Last Promotion and Attrition?
c. It's difficult to deduce anything based on the visualization

## Automated Machine Learning with H20 (II)



```{r}
library(tidyverse)
library(readxl)
library(h2o)
library(rsample)
library(recipes)





############ STEP # 1 ############################




product_backorder_tbl          <- read_csv("product_backorders.csv")

set.seed(seed = 1113)
split_obj                       <- rsample::initial_split(product_backorder_tbl, prop = 0.85)
train_readable_tbl              <- training(split_obj)
test_readable_tbl               <- testing(split_obj)

recipe_obj <- recipe(went_on_backorder ~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>% 
  prep()

train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)















############ STEP # 2 ############################




# Modeling
h2o.init()

split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(test_tbl)

y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)






############ STEP # 3 ############################




#?h2o.automl

automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 300,
  nfolds            = 5 
)




################Step 4 View the leaderboard##############


typeof(automl_models_h2o)

slotNames(automl_models_h2o)

automl_models_h2o@leaderboard

automl_models_h2o@leader


extract_h2o_model_name_by_position <- function(h2o_leaderboard, n = 1, verbose = T) {
  
  model_name <- h2o_leaderboard %>%
    as_tibble() %>%
    slice(n) %>%
    pull(model_id)
  
  if (verbose) message(model_name)
  
  return(model_name)
  
}


automl_models_h2o@leaderboard %>% 
  extract_h2o_model_name_by_position(14) %>% 
  h2o.getModel() %>%






################ Saving & Loading H2O models Step#5 ###############


  h2o.saveModel(path = "04_Modeling/h20_models/challenge")


h2o.loadModel("04_Modeling/h20_models/challenge/GBM_grid__1_AutoML_20210531_150000_model_3")

############### Step 5 Predicting using Leader Model#####################


stacked_ensemble_h2o <- h2o.loadModel("04_Modeling/h20_models/challenge/GBM_grid__1_AutoML_20210531_150000_model_3")
stacked_ensemble_h2o

predictions <- h2o.predict(stacked_ensemble_h2o, newdata = as.h2o(test_tbl))

typeof(predictions)

predictions_tbl_2 <- predictions %>% as_tibble()
predictions_tbl_2

################### end ######################
```
